### 2023-06-23 chapter_2/src/appendix.qmd
oops, forgot ppc's

@@

names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_intercept" = "Intercept"
    , "b_dem_vote_share" = "Democratic vote share (%)"
  )
)

```

>>>>

<!-- 
NOTE TO SELF

NEED TO REWRITE SOME OF THIS TO ACCOUNT FOR BETTER PERFORMANCE AFTER LOCATION-FXS
-->

@@

names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_intercept" = "Intercept"
    , "b_dem_vote_share" = "Democratic vote share (%)"
  )
)
```

### Posterior predictive checks

```{r}
#| label: fig-hypothesis-5-ppc
#| tbl-cap: Posterior Predictive checks for $H_5$

list_ppc[["h_5"]][["red"]]
list_ppc[["h_5"]][["blue"]]
```
